HO unification from object language to meta language

### 2024-03-20 paper/main.tex
Update latex

@@

La deduplicate eta:
  - viene chiamata che della forma [variable] -> [eta1] e [variable] -> [eta2] (a destra non c'è mai un termine con testa rigida)
  - i due termini a dx vengono unificati con la unif e uno dei due link viene buttato
    -> si mettono più lambda 
  - dopo l'unificazione rimane un link [variabile] -> [etaX] e quando
    risolviamo un eta-link, allora dobbiamo eta-espandere qb il termine di sinistra per
    poterlo  unifcare con quello di dx.

@@

\begin{elpicode}
  f = flam x\ flam y\ fapp[F, (X x), y] % $f = \lambda x.\lambda y.F (X x) y$
\end{elpicode}

\noindent
from the subsitution $\rho = \{X \mapsto \lambda x.x\}$.

\noindent
\otext{The following goal: \elpiIn{X = lam x\ x, app[X, a] = a}}
\otext{We use links-beta}

>>>>

\newcommand{\linketaM}[3]{\texttt{#1 |- #2 =$\eta$= #3}}
\newcommand{\linkbetaM}[3]{\texttt{#1 |- #2 =$\beta$= #3}}

@@

\begin{textcode}
  La deduplicate eta:
  - viene chiamata che della forma [variable] -> [eta1] e [variable] -> [eta2] 
    (a destra non c'è mai un termine con testa rigida)
  - i due termini a dx vengono unificati con la unif e uno dei due link viene buttato
    NOTA!! A dx abbiamo sempre un termine della forma lam x.VAR x!!!
    Altrimenti il link sarebbe stato risolto!!
  - dopo l'unificazione rimane un link [variabile] -> [etaX] 
  - nella progress-eta, se a sx abbiamo una constante o un'app, allora eta-espandiamo
    di uno per poter unificare con il termine di dx.
\end{textcode}

@@

\begin{elpicode}
  f = flam x\ fapp[F, (X x), a] % $f = \lambda x.F (X x) a$
\end{elpicode}

\noindent
under the subsitution $\rho = \{X \mapsto \lambda x.x\}$.

\noindent
The links generated from this unification problem are:

\begin{textcode}
X ~$\mapsto$~ X1; F ~$\mapsto$~ X2 % The mappings
  ~$\vdash$~ X0   =~$\eta$~= x\ `X3 x'
x ~$\vdash$~ X3 x =~$\beta$~= X2 `X1 x' a
\end{textcode}

\noindent
where the first link is a \linketa between the variable \texttt{X0}, representing
the right side of the unification problem (it is a \maybeeta) and
\texttt{X3}; and a \linkbeta between the variable \texttt{X3} and the subterm
\texttt{c0\textbackslash\ X2 `X1 c0' a} (it is a \maybebeta).
The substitution tells that \textIn{x ~$\vdash$~ X1 x = x}.

We can now represent the \hrun execution from this configuration which will, at
first, dereference all the links, and then try to solve them. The only link
being modified is the second one, which is set to \textIn{X3 x =~$\beta$~= X2
x a}. The $rhs$ of the link has now a variable which is partially in the PF,
we can therefore remove the original \linkbeta and replace it with the following 
couple on links:

\begin{textcode}
  ~$\vdash$~ X1   =~$\eta$~= x\ `X4 x'
x ~$\vdash$~ X3 x =~$\beta$~= x\ `X4 x' a
\end{textcode}

By these links we say that \texttt{X1} is now $\eta$-linked to a fresh variable
\texttt{X4} with arity one. This new variable is used in the new \linkbeta where
the name \texttt{x} is in its scope. This allows
